ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-25 pyked.tex
PyKED shouldn't be tt
Switch citations to autocite and update bib

\usepackage{todonotes}
\newcommand\ck{ChemKED}
\newcommand\pk{\texttt{PyKED}}
\usepackage[inline]{enumitem}
\setlist{noitemsep}
%======================================================================
\addbibresource{pyked.bib}
%======================================================================
\newcommand\papertopic{Reaction Kinetics}
%======================================================================

@@

The combustion\slash chemical kinetics community lacks an accepted, commonly used
standard for recording and sharing data from fundamental combustion experiments.
Interestingly, this contrasts the situation for chemical kinetic models, where the
CHEMKIN~\cite{Kee:1996ck} format dominates. Competing standards such as the
Cantera~\cite{Cantera:2.3.0} CTI format or FlameMaster lag behind considerably, although
use of the former continually grows due to Cantera's open availability.\todo{add flamemaster citation}{}
Similarly,

@@

While the community has not widely adopted a standard format,
---most notably, Frenklach developed the PrIMe (\textbf{Pr}ocess \textbf{I}nformatics
\textbf{M}od\textbf{e}l) data format~\cite{Frenklach:2007bm,You:2011hy} and an associated
online database, the PrIMe Data Warehouse~\cite{PrIMe}.

More recently, Varga et al.~\cite{Varga2015a,Varga2015b} developed the \texttt{ReSpecTh} standard,
an XML-based format that builds on, and is compatible with, PrIMe.

@@

Niemeyer recently introduced an initial version of the \ck{} format~\cite{Niemeyer:2016wf},
and in this work we further formalize and develop the standard. We also discuss a related
Python software tool for validating and working with \ck{} files: \pk{}.

@@

\pk{} relies on well-established scientific Python software tools.
These include NumPy~\cite{vanderWalt:2011np} for array manipulation, Pint~\cite{Grecco2016} for
interpreting and converting between units, \texttt{ruamel.yaml} for parsing YAML files,\todo{needs ref}{}
Cerberus for validating \ck{} files\todo{needs ref}{},
and pytest~\cite{pytest:3.0.1} for unit testing.
Travis-CI~\cite{Travis2016} also provides continuous integration testing.

>>>>

\usepackage{todonotes}
\newcommand\ck{ChemKED}
\newcommand\pk{PyKED}
\usepackage[inline]{enumitem}
\setlist{noitemsep}
%======================================================================
\addbibresource{pyked.bib}
%======================================================================
\newcommand\papertopic{Reaction Kinetics}
%======================================================================

@@

The combustion\slash chemical kinetics community lacks an accepted, commonly used
standard for recording and sharing data from fundamental combustion experiments.
Interestingly, this contrasts the situation for chemical kinetic models, where the
CHEMKIN~\autocite{Kee:1996ck} format dominates. Competing standards such as the
Cantera~\autocite{Cantera:2.3.0} CTI format or FlameMaster lag behind considerably, although
use of the former continually grows due to Cantera's open availability.\todo{add flamemaster citation}{}
Similarly,

@@

While the community has not widely adopted a standard format,
---most notably, Frenklach developed the PrIMe (\textbf{Pr}ocess \textbf{I}nformatics
\textbf{M}od\textbf{e}l) data format~\autocite{Frenklach:2007bm,You:2011hy} and an associated
online database, the PrIMe Data Warehouse~\autocite{PrIMe}.

More recently, Varga et al.~\autocite{Varga2015a,Varga2015b} developed the \texttt{ReSpecTh} standard,
an XML-based format that builds on, and is compatible with, PrIMe.

@@

Niemeyer recently introduced an initial version of the \ck{} format~\autocite{Niemeyer:2016wf},
and in this work we further formalize and develop the standard. We also discuss a related
Python software tool for validating and working with \ck{} files: \pk{}.

@@

\pk{} relies on well-established scientific Python software tools. These include
NumPy~\autocite{vanderWalt:2011np} for array manipulation,
Pint~\autocite{Grecco2016} for interpreting and converting between units,
\texttt{ruamel.yaml} for parsing YAML files,\todo{needs ref}{} Cerberus for
validating \ck{} files~\autocite{cerberus}, and pytest~\autocite{pytest:3.0.1}
for unit testing. Travis-CI~\autocite{Travis2016} also provides continuous
integration testing.
